### 2018-11-29 Sections/economics_of_the_quantum_internet.tex
roadmap

\dropcap{I}{n} the same scenario as before, where compute-time is being licensed out to end-users, the hardware owners return over a single unit of time equates to the cost of computation over that period.

Let $L(t)$ be the dollar-value of utilising the network's computing resources for a single unit of time. This is obtained as the return made on the value of the network per FLOP,
\begin{postulate}[Cost of computation]\label{post:cost_comp}
The efficient-market dollar-value of a computation for a single unit of time at time $t$, per FLOP is,
\begin{align}\index{Cost of computation}
	L(t) &= \frac{e^{\gamma_\mathrm{ror}} P(t)}{V(t)} \nonumber\\
	&= \frac{e^{\gamma_\mathrm{ror}} C_0{\gamma_C}^{-t}}{\chi_\mathrm{sc}(N_0 {\gamma_N}^t)}.
\end{align}
\end{postulate}
which implies,
\begin{postulate}[Spot price of computation]\index{Spot price of computation} The present-day (\mbox{$t=0$}) spot price of a computation per FLOP is,
\begin{align}
L(0) = \frac{e^{\gamma_\mathrm{ror}}C_0}{\chi_\mathrm{sc}(N_0)}.	
\end{align}
\end{postulate}
That is, the value of computations simply approximates the return on initial hardware investment, scaled by its initial computational power, as is intuitively expected.

@@

This effectively implies that some users pay more for computation (in terms of return on investment\index{Return on investment (RoI)}) than others. While the objective cost of computation is conceptually simple to model (as performed in a rudimentary fashion in Sec.~\ref{sec:cost_of_comp}), the subjective cost is a highly non-trivial one. It will depend heavily on the scaling function of the algorithm run by a user, and of course the economic objectives of their computation -- a quantum simulation algorithm executed by an R\&D lab\index{R\&D} is likely to be of greater monetary value than and undergrad using his university's resources to execute the same task for completing an assignment!

>>>>

\dropcap{I}{n} the same scenario as before, where compute-time is being licensed out to end-users, the hardware owner's return over a single unit of time equates to the cost of computation over that period.

Let $L(t)$ be the dollar-value of utilising the network's computing resources for a single unit of time. This is obtained as the return made on the value of the network per FLOP,
\begin{postulate}[Cost of computation]\label{post:cost_comp}
The efficient-market dollar-value of a computation for a single unit of time at time $t$, per FLOP is,
\begin{align}\index{Cost of computation}
	L(t) &= \frac{e^{\gamma_\mathrm{ror}} V(t)}{P(t)} \nonumber\\
	&= \frac{e^{\gamma_\mathrm{ror}} C_0{\gamma_C}^{-t}}{\chi_\mathrm{sc}(N_0 {\gamma_N}^t)}.
\end{align}
\end{postulate}
which implies,
\begin{postulate}[Spot price of computation]\index{Spot price of computation} The present-day (\mbox{$t=0$}) spot price of a computation per FLOP is,
\begin{align}
L(0) = \frac{e^{\gamma_\mathrm{ror}}C_0}{\chi_\mathrm{sc}(N_0)}.	
\end{align}
\end{postulate}
That is, the value of computations simply approximates the return on initial hardware investment, scaled by its initial computational power, as is intuitively expected.

@@

This effectively implies that some users pay more for computation (in terms of return on investment\index{Return on investment (RoI)}) than others. While the objective cost of computation is conceptually simple to model (as performed in a rudimentary fashion in Sec.~\ref{sec:cost_of_comp}), the subjective cost is a highly non-trivial one. It will depend heavily on the scaling function of the algorithm run by a user, and of course the economic objectives of their computation -- a quantum simulation algorithm executed by an R\&D lab\index{R\&D} is likely to be of greater monetary value than an undergrad using his university's resources to execute the same task for completing an assignment!
